---
title: "Interactive penguins"
author: "Alia Ajina"
date: "10/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Packages
library(tidyverse)
library(palmerpenguins)
library(plotly)
library(DT)

# install.packages("package_name") in console
```



Scatterplot of penguins flipper_length_mm (x-axis) versus body_mass_g (y-axis), with points having different colors based on species

Use "View(penguins)" to see the dataset.

We are asking this to create this graph and store it, not asking it to show it to us, if we wanted it to show up we would have to call it by typing in it's name below : 
" penguins_graph # bringing the graph up" below the code

ggplotly allows the graph to become interactive

```{r}
penguins_graph <- ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species)) 

ggplotly(penguins_graph)
```

How to create a nice table:
searchable table
and continues it's interactiveability in the knitted document

```{r}
datatable(penguins)
```

